Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-03-21 paperDistance/paper.tex
toy example caption

\section{Why does this work?}
\begin{figure}
\centering
  \includegraphics[width=\textwidth]{toy.png}
\caption{Why does this work: Fitting a line}
\label{fig:line}
\end{figure}

@@

So
\begin{eqnarray}
p(y_{true,n} \given y_n, \tilde{\sigma}_n) &=& p(y_n \given y_{true,n}, \sigma_n)\,p(y_{true,n}) \\
p(y_n \given y_{true,n}, \sigma_n) &=& \mathcal{N}(y_n \given y_{true,n}, \sigma_n) \\
p(y_{true,n}) &=& \mathcal{N}(y_{true,n} \given \hat{m}\, x_n + \hat{b}, \hat{t})
\label{eq:toyBayes}
\end{eqnarray}

>>>>

\section{Why does this work?}
\begin{figure}
\centering
  \includegraphics[width=\textwidth]{toy.png}
\caption{ {\bf Why does this work}: An example of generating posterior beliefs of noisy data by using the denoised distribution of data as a prior. The left panel is 1024 realizations of noisy data drawn from the gaussian distribution represented by the $1\sigma$ red lines shown in the center panel. The black points are 5 randomly chosen data to highlight the method. The blue lines in the center panel represent the MML best estimate for the underlying distribution, which denoises the data. The blue points in the center panel represent the posterior belief of the true values of the noisy black points, and the red points represent the actual true values. The right panel shows the posterior belief of the true value for all the points. They are colored by the measurement variance showing that data with larger measured variance are more influenced by the prior and lie towards the center of the MML distribution, or prior. Where as more certain measurements tend to lie closer to their measured value. The blue points are better than the black for doing stuff.}
\label{fig:line}
\end{figure}

@@

So using Bayes theorem
\begin{eqnarray}
p(y_{true,n} \given y_n, \tilde{\sigma}_n) &=& p(y_n \given y_{true,n}, \sigma_n)\,p(y_{true,n}) \\
p(y_n \given y_{true,n}, \sigma_n) &=& \mathcal{N}(y_n \given y_{true,n}, \sigma_n) \\
p(y_{true,n}) &=& \mathcal{N}(y_{true,n} \given \hat{m}\, x_n + \hat{b}, \hat{t})
\label{eq:toyBayes}
\end{eqnarray}
